Efficient Development Framework with mruby \\for Embedded Systems

### 2016-06-07 CPSNA2016/paper.tex
update CPSNA2016

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
\title{Efficient Development Framework with mruby for Embedded Systems}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\section{Introduction}
Currently, embedded systems must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
To improve development efficiency, in the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device using the Bluetooth loader.
% Note that RiteVM is the Ruby VM specifically designed for embedded systems.
The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., VMs designed for mruby) and allows developers to program multitasking more easily than the current version of mruby on TECS.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality of mruby on TECS, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.

@@

\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
Bytecode on the host is transferred and received.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.

@@

Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.

@@

\subsection{Improving Development Efficiency by Bluetooth Loader}
The Bluetooth loader for mruby bytecode can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
This shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

\section{Related Work}
\label{sec:Related work}
Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

>>>>

%
% File: paper.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference]{IEEEtran/IEEEtran/IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% \title{Efficient Devlopment Framework applied Scripting Language for Embedded Systems}
\title{Efficient Development Framework with mruby \\for Embedded Systems}
\author{\IEEEauthorblockN{Takuro Yamamoto}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
\and\IEEEauthorblockN{Hiroshi Oyama}\IEEEauthorblockA{OKUMA Corporation}
\and\IEEEauthorblockN{Takuya Azumi}\IEEEauthorblockA{Graduate School of Engineering Science,\\Osaka University}
}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale such by cyber physical systems.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., mruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives a transferred mruby bytecode from a host, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

% \keywords{embedded software; scripting language; component-based development}
\begin{IEEEkeywords}
embedded software; scripting language; component-based development
\end{IEEEkeywords}

\section{Introduction}
Currently, embedded systems such as Cyber Physical Systems must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

This paper proposes an extended framework of mruby on TECS that comprises a Bluetooth loader for mruby bytecode and a RiteVM scheduler for fairly executing mruby programs.
In the proposed framework, developers need to implement the platform on a storage device only once at the beginning and can transfer mruby application programs from a host to a target device via Bluetooth.
% Note that RiteVM is the Ruby VM specifically designed for embedded systems.
The RiteVM scheduler manages the execution of multiple RiteVMs (i.e., mruby VM) and allows developers to program multitasking more easily than the current version of mruby on TECS.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the complete software should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once.

@@

\subsubsection{RiteVM Component with Bluetooth Loader}
The proposed framework provides a RiteVM with a Bluetooth loader as a TECS component.
This component is an extended RiteVM component described in \cite{par:mrubyonTECS}.
It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader.
Figure \ref{fig:control_flow} shows the process flow for executing an mruby program on the RiteVM component with the Bluetooth loader for mruby bytecode, such as RiteVMBluetooth1.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.
The main tRiteVMBluetooth code is shown in Figure \ref{maincode_mrubybluetooth}.

@@

@@

\subsection{Improving Development Efficiency by Bluetooth Loader}
The Bluetooth loader can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=4.0cm,width=8.6cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time with Singletasking, Co-routine, and Proposed Multitasking}
In Figure \ref{fig:comparison_s_c_m}, the periodic time of the periodic handler for multitasking is 1 msec.
This shows that the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

\section{Related Work}
\label{sec:Related work}
Open-source runtime systems for scripting languages have been proposed such python-on-a-chip \cite{url:python-on-a-chip}, Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.
